# Task

Read in global gender inequality data
Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019
Share it with the World on GitHub
Add you repository URL to the circulated spreadsheet


## packages()
```{r message=FALSE, warning=FALSE}
library(sf)
library(here)
library(raster)
library(terra)
library(fs)
library(tidyverse)
library(ggplot2)
library(plotly)
library(janitor)
library(tmap)
library(tmaptools)
library(countrycode)
```
## read in files
```{r}
alldata_90_21 <- read.csv("orignal_data\\HDR21-22_Composite_indices_complete_time_series.csv",header = TRUE, sep = ",",
                          encoding = "latin1",na= "NULL")

world_shape <- st_read("orignal_data\\World_Countries_(Generalized)\\World_Countries__Generalized_.shp")
```
## clear names and select required colums
```{r}
gender_inqidx_10_19 <- alldata_90_21 %>%
  clean_names() %>% 
  select(iso3,country,hdicode,region,gii_2010,gii_2019)
```
## filter the unrequired data
```{r}
gender_inqidx_1019 <- gender_inqidx_10_19 %>% 
  slice(1:195)

```
## check data type
```{r}
class(gender_inqidx_1019)
Datatypelist <- gender_inqidx_1019 %>%  
  summarise_all(class) %>% 
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist

```
## creating a new column show the difference
```{r}
gdr_inqidx_dif1019 <- gender_inqidx_1019 %>%
  mutate(difference_1019 = gii_2019 - gii_2010)
  
```
## convert countrycode to ensure the uniformity
?countrycode
```{r}
dif1019_match_shp <- gdr_inqidx_dif1019 %>% 
  mutate(iso2 = countrycode(gdr_inqidx_dif1019$iso3, origin = 'iso3c', destination = 'iso2c'))
```
## join the csv and shp
```{r}
dif1019_join <- world_shape %>% 
  left_join(., 
            dif1019_match_shp,
            by = c("ISO" = "iso2"))
```





